a and generators

### 2022-07-25 documentos/answer_referees_PRA.txt

Dear Editor,

We are happy to receive positive feedback from the referees. The points
raised by the referees are answer in what follows.

Answer to the First Referee  {{{

*********************************************************************
1, Is there any difference or they are interchangeable between Pauli
diagonal operation and Pauli diagonal map? Please define them clearly
in the text when they first appear.

Answer:
There is no difference. We have replaced all occurrences
of "PCE operation" with "PCE map" (or similar), see list of changes.

*********************************************************************
2, It is clear that the channel Eq. (12) defines a super operator
acting on any B(H), but for the Choi matrix in Eq. (13), why it is a
super-operator?

Answer:
We have changed the wording. We now call D_N a "matrix"
(as it is a Choi matrix) instead of a superoperator.

*********************************************************************
3, I find this sentence “Let the components of \beta be such that
\beta_l =\beta\delta_lk for a particular particle index k, with \beta
such that a_\alpha_k\beta  = 1” rather confusing.

Answer:
We agree, the statement was confusing. We are now providing a 
new (and hopefully better) explanation.

*********************************************************************
4, Although two mathematical decoherence models are given, the
physical motivation of studying this general many qubit PCE channel is
not quite clear? It also would be better to motivate it in the
beginning.

Answer:
This paper grew from the sheer curiosity of why, for a single qubit, some
projections are allowed and others not. After some time, the beautiful 
mathematical structure presented in this paper appeared. Indeed some 
motivations might be presented, however the main one is simply to gain a 
deeper understanding of quantum channels in a multiparticle setting.
We have tried to put together an introduction that reflects that point 
of view, and we wish to keep it that way. However if further insistence 
on this point is made by the referee we can add some sentences in the
introduction.

*********************************************************************
I feel like there is a simple example of the PCE channel: it might be
called the stabilizer state PCE, e.g., N qubit stabilizer state,
erasing one stabilizer generator could give another stabilizer state,
and the remaining Pauli component is obviously 2^{N-1}, satisfying the
2^K components preserving statement. Moreover, in this case erasing
any one stabilizer generator will preserve exactly half the Pauli
components, as generator for all PCE channel?

Since stabilizer states are very useful in quantum computation,
perhaps it is a good practical motivation to study this PCE channel,
as long as they have a solid connection?

Answer:
The connection with stabilizer states might be interesting, given 
that for both stabilizer states and PCEs, Pauli strings play 
a prominent roll in there definitions. We have added a paragraph 
at the end of section III pointing out this possible relation.

*********************************************************************
}}}

Answer to of the Second Referee {{{
----------------------------------------------------------------------

*********************************************************************
Could you shed more light on the physical motivation for this study?

Answer:
The other referee has brought up the same question. We kindly refer the referee
to the paragraph in question in which we prefer to leave the motivation as it
stands. 
*********************************************************************
How do you think the scheme would work for qudits in dimensions of
Hilbert spaces which are not 2^n? Of course, I understand that your
results are pertinent to basis of Pauli tensors, but I am curious to
know your thoughts on the same.

For dimensions $d$ that allow $d+1$ maximally unbiased bases, one can
construct generalized Pauli channels. In those cases, do you think
your results could be extended in some way?

Answer:
This is clearly an interesting question. The generalization is not totally 
direct, and requires some mathematical work.  This is why we did not
present results in this paper, however we will hopefully present a generalization 
for arbitrary dimension. Some care must be taken as some results depend on the
field structure of the set {0,1}, which will not be available for arbitrary 
$d$.

*********************************************************************

}}}

List of changes {{{
* Between eq. (2) and eq. (3) we replaced 
    Not every such operation  is a quantum channel;
with 
    Not every such map  is a quantum channel;

* In the caption of figure 1, we replaced 
    ... and thus does not correspond to a quantum operation.
with 
    ... and thus does not correspond to a quantum channel.

* After eq. (6), we replaced 
    In addition, for the operation to be trace preserving...
with 
    In addition, for the map to be trace preserving...

* In that same paragraph, we replaced 
    We shall refer to the map  $xx$, with arbitrary values of $\taus$ (only
    restricted by complete positivity) as {\it Pauli diagonal operations}.  
with 
    We shall refer to the map  $xx$, with arbitrary values of $\taus$ (only
    restricted by complete positivity) as {\it Pauli diagonal maps}.

* Before eq. (13) we replaced 
    The matrix representation of the map corresponding to a Pauli diagonal operation is...
with 
    The matrix representation of the map corresponding to a Pauli diagonal map is...

* After eq. (13) we replaced 
    This superoperator is again diagonal in the (multi-qubit) Pauli basis...
with 
    This matrix is again diagonal in the (multi-qubit) Pauli basis...

* We changed the paragraph leading to eq. (23) from
    Let us now work out the nature of the aforementioned connection.  Let the
    components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
    particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
    Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
    belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
    indeed holds. However, for such a choice
    of $\vbeta$ the above relation reduces to 
to
    Let us now work out the nature of the aforementioned connection.  For
    arbitrary $k$ we define a vector $\vbeta_k$ such that
    $\vbeta_k\in\Phi(\vec\alpha)$ as follows: $\vbeta_k$ is zero everywhere except
    for the $k$'th coordinate, which takes a value $\beta$ such that
    $\sa_{\alpha_k\beta}=1$. Since $\sa_{\alpha 0}=1$ for any $\alpha$, this
    particular choice of $\vbeta$ indeed belongs to  $\Phi(\vec\alpha)$, so
    that if \eref{eq:coneccion:dos:indices:A} holds for all
    $\vbeta\in\Phi(\vec\alpha)$, it must hold for that particular $\vbeta_k$,
    which leads to:

* At the end of section III we added the following paragraph:
    Finally, let us point out the following: if we wish to specify a PCE
    channel explicitly, the naive way to proceed would be simply to list all the
    Pauli components which are not erased. This requires in general, however, an
    exponential amount of information: that is, if the system has $N$ qubits, we
    generally require of the order of $2^N$ bits to do this. If, on the other hand,
    we take advantage of the vector space structure of a PCE channel, we only need
    to specify a basis. Since a basis consists of $N$ vectors of length $N$, the
    information required is only of $N^2$ bits, so that we have obtained a very
    substantial improvement by exploiting the total positivity. This is reminiscent
    of a rather similar effect in {\em stabilizer states\/} which can also be
    specified by $N^2$ bits, as opposed to an exponentially large number of basis
    coefficients for arbitrary states.  A stabilizer state is one which is the
    common eigenvector to the eigenvalue 1 of a set of $N$ commuting 
    Pauli strings.  The similarity is highly intriguing, and
    potentially of interest, since stabilizer states are of central importance in
    quantum error correction \cite{Gottesman1997}. 
}}}

Email, all {{{
Re: AS12227
    Pauli component erasing quantum channels
    by Jos\'e Alfredo de Leon, Alejandro Fonseca, Fran\c{c}ois Leyvraz, et
    al.

Dear Dr. Pineda,

The above manuscript has been reviewed by two of our referees. Comments
from the reports appear below.

These comments suggest that specific revisions of your manuscript are
in order. When you resubmit your manuscript, please include a summary
of the changes made and a succinct response to all recommendations or
criticisms contained in the reports.

Yours sincerely,

Mrs. Terre Arena (she/her/hers)
Senior Editorial Assistant
Physical Review A

----------------------------------------------------------------------
Report of the First Referee -- AS12227/de Leon
----------------------------------------------------------------------

This paper generalizes the single qubit channel as a concept of Pauli
component erasure channel, and extends it to the multi-qubit case.
Since the erasure map doesn’t always gives a valid quantum channel,
the authors try identifying the condition for the map to be CPTP,
which turns out to be related to the vector subspace of the Pauli
string set indices. Two simple mathematical decoherence model are also
introduced. This study is overall interesting. I give my comments and
questions in the following and would give my recommendation for
publication upon appropriately addressing them:

1, Is there any difference or they are interchangeable between Pauli
diagonal operation and Pauli diagonal map? Please define them clearly
in the text when they first appear.

2, It is clear that the channel Eq. (12) defines a super operator
acting on any B(H), but for the Choi matrix in Eq. (13), why it is a
super-operator?

3, I find this sentence “Let the components of \beta be such that
\beta_l =\beta\delta_lk for a particular particle index k, with \beta
such that a_\alpha_k\beta  = 1” rather confusing.

4, Although two mathematical decoherence models are given, the
physical motivation of studying this general many qubit PCE channel is
not quite clear? It also would be better to motivate it in the
beginning.

I feel like there is a simple example of the PCE channel: it might be
called the stabilizer state PCE, e.g., N qubit stabilizer state,
erasing one stabilizer generator could give another stabilizer state,
and the remaining Pauli component is obviously 2^{N-1}, satisfying the
2^K components preserving statement. Moreover, in this case erasing
any one stabilizer generator will preserve exactly half the Pauli
components, as generator for all PCE channel?

Since stabilizer states are very useful in quantum computation,
perhaps it is a good practical motivation to study this PCE channel,
as long as they have a solid connection?

----------------------------------------------------------------------
Report of the Second Referee -- AS12227/de Leon
----------------------------------------------------------------------

This is an interesting paper which is well articulated. However,
before I accept the same for publication, I have a few questions to
the authors.

Could you shed more light on the physical motivation for this study?

How do you think the scheme would work for qudits in dimensions of
Hilbert spaces which are not 2^n? Of course, I understand that your
results are pertinent to basis of Pauli tensors, but I am curious to
know your thoughts on the same.

For dimensions $d$ that allow $d+1$ maximally unbiased bases, one can
construct generalized Pauli channels. In those cases, do you think
your results could be extended in some way?
}}}

### 2022-07-25 documentos/math.tex
intro mas label a seccion
otra vez single-qubit
Cambios marcados
yet another quality commit
<<<<<<<<<<<<<<< HEAD

@@

We now construct the Choi matrix of a single qubit Pauli diagonal map

@@

% \janote{Cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
% modificó la frase que le sigue a este comentario.}

@@

%direct vectorization of $\sigma_{\vec \alpha}$

@@

map corresponding to a Pauli diagonal operation is 

@@

This superoperator is again diagonal in the (multi-qubit) Pauli basis, with the 

@@

% After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis

>>>>

\label{sec:math}

@@

We now construct the Choi matrix of a single-qubit Pauli diagonal map

@@

@@

@@

map corresponding to a Pauli diagonal map is 

@@

This matrix is again diagonal in the (multi-qubit) Pauli basis, with the 

@@

% After several steps, it is possible to prove that analogously to the  case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis

### 2022-07-25 documentos/pce.tex
<<<<<<<<<<<<<<< HEAD

a quantum operation.

@@

% Thus, i
In general, a Pauli component erasing (PCE) map is a map
%  Pauli diagonal operation
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
In addition, for the operation to be trace preserving, it is required that $\tau_{\vec
0}=1$. 
It is worth noticing that, as for the single-qubit case, not all PCE maps are
quantum operations. 
On the other hand, constructing and
evaluating the conditions for complete positivity is non-trivial and is the main
problem addressed in this paper.
We shall refer to the map  $\paulicomponents \mapsto \taus \paulicomponents$, 
with arbitrary values of 
% but allow the 
$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal operations}.

>>>>

a quantum channel.

@@

% Thus, i
In general, a Pauli component erasing (PCE) map is a map
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
In addition, for the operation to be trace preserving, it is required that $\tau_{\vec
0}=1$. 
It is worth noticing that, as for the single-qubit case, not all PCE maps are
quantum operations. 
On the other hand, constructing and
evaluating the conditions for complete positivity is non-trivial and is the main
problem addressed in this paper.
We shall refer to the map  $\paulicomponents \mapsto \taus \paulicomponents$, 
with arbitrary values of 
$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal maps}.

### 2022-07-25 documentos/vector_space.tex
yet another quality commit
<<<<<<<<<<<<<<< HEAD

Let us now work out the nature of the aforementioned connection.  Let the
components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
indeed holds. However, for such \flnote{a choice} \sout{election}
of $\vbeta$ the above relation reduces
to 
\begin{equation}
\sa_{\beta\gamma_k}=\sa_{\beta\gamma_k^\prime}
\label{eq:14}
\end{equation}
for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$.  One can verify, by
working out the different cases, that \eref{eq:14} is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha_k\oplus{}\gamma_k
\label{eq:oplus}
\end{equation}
where the $\oplus{}$ denotes the operation of the Klein group; see Figure
\ref{tab:1} for a detailed description. 
\par
% }}}
% Espacio vectorial {{{

@@

% }}}

>>>>

Let us now work out the nature of the aforementioned connection.  For arbitrary
$k$ we define a vector $\vbeta_k$ such that $\vbeta_k\in\Phi(\vec\alpha)$ as
follows: $\vbeta_k$ is zero everywhere except
for the $k$'th coordinate, which takes a value $\beta$ such that  $\sa_{\alpha_k\beta}=1$. Since 
$\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
indeed belongs to  $\Phi(\vec\alpha)$, so that if \eref{eq:coneccion:dos:indices:A} holds for 
all $\vbeta\in\Phi(\vec\alpha)$, it must hold for that particular $\vbeta_k$, which leads to:
% 
% Let us now work out the nature of the aforementioned connection.  Let the
% components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
% particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
% Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
% belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
% indeed holds. However, for such a choice
% of $\vbeta$ the above relation reduces
% to 
\begin{equation}
\sa_{\beta\gamma_k}=\sa_{\beta\gamma_k^\prime}
\label{eq:14}
\end{equation}
for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$.  One can verify, by
working out the different cases, that \eref{eq:14} is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha_k\oplus{}\gamma_k
\label{eq:oplus}
\end{equation}
where the $\oplus{}$ denotes the operation of the Klein group; see Figure
\ref{tab:1} for a detailed description. 
\par
% }}}
% Espacio vectorial {{{

@@

% Stabilizer codes {{{
Finally, let us point out the following: if we wish to specify a PCE
channel explicitly, the naive way to proceed would be simply to list all the
Pauli components which are not erased. This requires in general, however, an
exponential amount of information: that is, if the system has $N$ qubits, we
generally require of the order of $2^N$ bits to do this. If, on the other hand,
we take advantage of the vector space structure of a PCE channel, we only need
to specify a basis. Since a basis consists of $N$ vectors of length $N$, the
information required is only of $N^2$ bits, so that we have obtained a very
substantial improvement by exploiting the total positivity. This is reminiscent
of a rather similar effect in {\em stabilizer states\/} which can also be
specified by $N^2$ bits, as opposed to an exponentially large number of basis
coefficients for arbitrary states.  A stabilizer state is one which is the
common eigenvector to the eigenvalue 1 of a set of $N$ commuting 
Pauli strings.  The similarity is highly intriguing, and
potentially of interest, since stabilizer states are of central importance in
quantum error correction \cite{Gottesman1997}.

% }}}
% }}}
